State of the Art in Scientific Workflow Systems

### 2014-06-04 text/galaxy.tex
dded a sentence about galaxy

\paragraph{Galaxy Portal/JSON} Galaxy~\cite{blankenberg-vonkuster-etal:2010} is a
SWE developed at the Penn State University, Pennsilvania. It provides a
webportal based environment to build complex pipelines from an available
repository of tools (\textit{http://g2.bx.psu.edu}).  Galaxy is currently used
mainly by bioinformatics community. Users can extend the tool repository
provided by Galaxy using their own Galaxy server. One of the major use of
Galaxy is to achieve a mix and match of data analysis tools in order to analyze
a vast repository of genome based database. Galaxy offers a web-based,
interactive platform for data analysis via reusable and reproducible workflows.
While excelling in the usability aspects, the Galaxy environment has a limited
parallelism capabilities and a small number of existing implementations for
interfacing with diverse, scalable computing infrastructures. The user can draw
workflows in which multiple copies of a task are created to operate on multiple
inputs at once, but this is not a scalable approach.

>>>>

\paragraph{Galaxy Portal/JSON} Galaxy~\cite{blankenberg-vonkuster-etal:2010} is a
SWE developed at the Penn State University, Pennsylvania. It provides a
web-based portal environment to build complex pipelines from an available
repository of processors called tools within Galaxy project
(\textit{http://g2.bx.psu.edu}).  Galaxy is currently used mainly by
bioinformatics community. Users can contribute and extend the tool repository
provided by Galaxy using a hosting server. One of the major use of Galaxy is to
achieve a mix and match of data analysis tools in order to analyze a vast
repository of genome based database. Galaxy offers a web-based, interactive
platform for data analysis via reusable and reproducible workflows.  While
excelling in the usability aspects, the Galaxy environment has a limited
parallelism expression capabilities and a small number of existing
implementations for interfacing with diverse, scalable computing
infrastructures. For instance, it is hard to express the commonly found
\texttt{foreach} parallel expression using Galaxy's visual interface. The user
can draw workflows in which multiple copies of a task are created to operate on
multiple inputs at once. However, workflows tend to get cluttered quickly and
is not scalable to large-scale computations.
